---
title: "k_anom_sql"
output: html_document
---

# Environment

```{r}
library(RPostgreSQL)
library(ssh)
library(tidyverse)
library(data.table)
library(purrr)
library(lubridate)
library(magrittr)
```



# Extracting data from p_zero_phi

```{r}
# Execute the query
demog_phi <- dbGetQuery(pg_con, "SELECT * FROM p_zero_phi.demog_phi")
# deid_keys <- dbGetQuery(pg_con, "SELECT * FROM p_zero_phi.deid_keys")
stay_events_phi <- dbGetQuery(pg_con, "SELECT * FROM p_zero_phi.stay_events_phi")
diag_events_phi <- dbGetQuery(pg_con, "SELECT * FROM p_zero_phi.diag_events_phi")
```

# Creating k-anonimity dataframe

We are not making a difference between diag_type, therefore treating both diagnosis as equally sensible regardless of whether they are primary or secondary.

```{r}
demog_comp_phi <- merge(x=stay_events_phi%>%select(patient_id, hosp_stay_id, hosp_adm_date, hosp_mortality_bin),
                        y=demog_phi%>%select(patient_id,birth_date,sex,nation_ref),by="patient_id")

demog_comp_phi <- merge(x=demog_comp_phi,
                        y=diag_events_phi%>%select(hosp_stay_id,icd,diag_type,reg_date), by="hosp_stay_id")

demog_comp_phi$age<-round(as.numeric(difftime(demog_comp_phi$hosp_adm_date, demog_comp_phi$birth_date, unit="weeks"))/52.25,0)

# we create the 'line' column as an anchor, we will later be able to retrieve actual age, nation and info about the icd before lines were kanonimized
demog_comp_phi%<>%mutate(line=row_number())

demog_comp_phi%<>%select(hosp_stay_id, hosp_mortality_bin, sex, nation_ref, icd, age,diag_type,reg_date, line)
demog_comp_phi<-unique(demog_comp_phi)
```


# Calculating k_anonymity

It is important to consider the balance between the risk of reidentification and the clinical usefulness of the data. In the case of our database, which includes 57639 combinations of age, sex, and ICD, we have determined that a k-anonymity threshold of 2 is appropriate. This is because it strikes a balance between the risk of reidentification and the clinical usefulness of the data for research purposes.

In order to further reduce the risk of reidentification, we have implemented a risk-based iterative deidentification strategy that takes into account the likelihood of different types of adversaries attempting to reidentify patients in the database. This includes considering the risk of reidentification in the event that the database is made completely public, as well as the likelihood of different types of adversaries having access to the data and attempting to reidentify patients.

First, we will consider the "friendly researcher," who may accidentally reidentify an acquaintance in the dataset. To mitigate this risk, we will use statistical principles such as k-anonymity and l-diversity to ensure that individuals cannot be distinguished from at least k-1 other individuals in the database, and that there are at least l distinct values for a sensitive attribute within a group of persons with k-anonymity.

Next, we will consider the "rogue researcher," who may deliberately attempt to reidentify individuals using public information. To mitigate this risk, we will use contractual and governance processes such as an end-user license agreement and training on scientific integrity to ensure that researchers use the data ethically and responsibly.

Finally, we will consider the "rogue insurance company," who may illegally attempt to reidentify individuals using corporate data. To mitigate this risk, we will implement an access protocol for source data, an opt-out procedure, and education and delegation logs to further protect patient privacy.

Overall, our approach to deidentifying the data will consider the risk of reidentification by different types of adversaries and implement measures to ensure that the data is safe and clinically useful for research purposes. We will use statistical principles such as k-anonymity and l-diversity to protect the privacy of individuals in the dataset, while also implementing processes such as end-user license agreements and training on scientific integrity to ensure ethical use of the data. In addition, we will implement access protocols, opt-out procedures, and education and delegation logs to further protect patient privacy and mitigate the risk of reidentification by rogue actors.

In order to maintain the clinical usefulness of the data, we have also implemented processes such as an end-user license agreement and training on scientific integrity to ensure that the data is used ethically and responsibly. In addition, we have implemented an access protocol for source data, an opt-out procedure, and education and delegation logs to further protect patient privacy. Overall, our approach to deidentifying the data is designed to ensure that the data is both safe and clinically useful for research purposes.

```{r}
# Define the desired k-anonymity level
kanom_level <- 2

# define k anom columns that define a group
kanon_cols <- c("age", "sex", "hosp_mortality_bin", "icd")

# define unique identifier of each unit of analysis to calculate how many instances of this unique of this id do we have per group
unique_idfr<-"hosp_stay_id"

# Calculate the k-anonymity of each row
demog_comp_phi_extended <- demog_comp_phi %>%
  group_by(.dots = kanon_cols) %>% 
  mutate(k_anon = length(unique(!!sym(unique_idfr))))

nrow(demog_comp_phi_extended)
```

# Creating k-anonimity groups

```{r}
# Filter the data frame to select rows with k-anonymity greater than or equal to the desired level, this patients are safe enough and no further action needs to be taken
demog_comp_phi_safe <- demog_comp_phi_extended %>%
  filter(k_anon >= kanom_level)

# Filter the data frame to select rows with k-anonymity below the threshold
demog_comp_phi_risky <- demog_comp_phi_extended %>%
  filter(k_anon < kanom_level)

nrow(demog_comp_phi_safe)
nrow(demog_comp_phi_risky)
```

After this initial anonimization adress we end up with two datasets

- demog_comp_phi_safe : no further action required, data is safe.
- demog_comp_phi_risky : on this dataset we will apply a suppression approach by removing first age chararacters and for those not reaching enough k_anom threshold, we will continue removing ICD characters until desired threshold is reached.

# Increasing k-anonimity

## 1) Age Generalization

Removing digits from the age column may be a more clinically useful and effective way to increase the k-anonymity of a dataset when the threshold is 2.
  
Removing digits from the age column is a form of generalization, which is a technique used to increase the k-anonymity of a dataset. Generalization involves reducing the level of detail in a dataset by replacing specific values with more general ones. In this case, removing digits from the age column is a way to generalize the age values in the dataset, reducing the level of detail and increasing the k-anonymity.

In contrast, replacing characters in the ICD codes is a form of suppression, which involves removing or obscuring specific values in a dataset. Suppression is generally considered a less preferable option for increasing the k-anonymity of a dataset, as it results in a greater loss of information and may affect the clinical usefulness of the data.

Overall, removing digits from the age column is a more clinically useful and effective way to increase the k-anonymity of a dataset when the threshold is 2. By using generalization rather than suppression, we can maintain a higher level of detail in the dataset while still ensuring that the k-anonymity threshold is met.

!! TODO eda se elimina siempre de todo el paciente.

```{r}
# Cast age column to character
demog_comp_phi_risky_forage_general <- demog_comp_phi_risky


# Cast age column to character
demog_comp_phi_risky_forage_general <- demog_comp_phi_risky_forage_general %>%
  mutate(age = as.character(age))

# Remove k_anon column
demog_comp_phi_risky_forage_general <- demog_comp_phi_risky_forage_general %>%
  select(-k_anon)

# Remove one digit from the age column for rows with more than one digit
demog_comp_phi_risky_forage_general <- demog_comp_phi_risky_forage_general %>%
  mutate(age = if_else(nchar(age) > 1, paste0(substr(age, 1, nchar(age) - 1), "*"), age))

# Calculate the new k-anonymity of each row
demog_comp_phi_risky_forage_general <- demog_comp_phi_risky_forage_general %>%
  group_by(.dots = kanon_cols) %>% 
  mutate(k_anon = length(unique(!!sym(unique_idfr))))

# Filter the data frame to select rows with k-anonymity greater than or equal to the desired level, this patients are safe enough and no further action needs to be taken
demog_comp_phi_safe_age <- demog_comp_phi_risky_forage_general %>%
  filter(k_anon >= kanom_level)

# "age" column in  "demog_comp_phi_risky_forage_general" is restored when k_anon < kanom_level since after removing one digit  the kanom level is still not safed enough

# We Filter rows with k_anon < kanom_level (marked as risky) and select only necessary columns
demog_comp_phi_risky_age <- demog_comp_phi_risky_forage_general %>%
  filter(k_anon < kanom_level)

#create a df only with unique hospid and ages, then join by hosp adm
uniquehosp_ages<-unique(demog_comp_phi_risky[,c('line','age')])

demog_comp_phi_risky_age <- demog_comp_phi_risky_age %>%
  inner_join(uniquehosp_ages, by = c("line")) %>%
  select(hosp_stay_id,hosp_mortality_bin,sex,age.y,icd,k_anon,line) %>%
  rename("age" = "age.y")

# checksum of rows 
nrow(demog_comp_phi_risky_forage_general)
nrow(demog_comp_phi_safe_age)
nrow(demog_comp_phi_risky_age)
nrow(demog_comp_phi_safe_age)+nrow(demog_comp_phi_risky_age)
```

After this initial anonymization approach we end up with two datasets:

- demog_comp_phi_safe_age : no further action required, data is safe.
- demog_comp_phi_risky_age : on this dataset we will apply a suppression approach by removing ICD characters until desired threshold is reached.

## 2) ICD Chars Suppression

### ICD A: 1 Character removal

After we remove 1 digit from the age, for those patients who didn't rease a satisfying k-anonimity level just by removing 1 digit from their age, we continue removing characters from the ICD codes and we repeat this process until the k-anonymity of all rows is above the threshold, using a loop.

The following code will remove one character from the right of each ICD code, calculate the new k-anonymity of each row using the kanon_cols variables, and repeat this process until all rows have a k-anonymity above the threshold defined by the kanom_level variable.

ICD needs to have at least 3 characters, we cannot remove anything else from there, otherwise we canot map it to any description.

```{r}
# Remove one digit from the age column for rows with more than one digit
demog_comp_phi_risky_age_foricdA <- demog_comp_phi_risky_age %>%
   mutate(icd = ifelse(nchar(icd) > 3, paste0(substr(icd, 1, nchar(icd) - 1), ""), icd))

# Calculate the new k-anonymity of each row
demog_comp_phi_risky_age_foricdA <- demog_comp_phi_risky_age_foricdA %>%
  group_by(.dots = kanon_cols) %>% 
  mutate(k_anon = length(unique(!!sym(unique_idfr))))

# Filter the data frame to select rows with k-anonymity greater than or equal to the desired level, this patients are safe enough and no further action needs to be taken
demog_comp_phi_safe_icdA <- demog_comp_phi_risky_age_foricdA %>%
  filter(k_anon >= kanom_level)

# Filter the data frame to select rows with k-anonymity smaller than the desired level
demog_comp_phi_risky_icdA <- demog_comp_phi_risky_age_foricdA %>%
  filter(k_anon < kanom_level)

# checksum of rows 
nrow(demog_comp_phi_risky_age)
nrow(demog_comp_phi_safe_icdA)
nrow(demog_comp_phi_risky_icdA)
nrow(demog_comp_phi_safe_icdA)+
nrow(demog_comp_phi_risky_icdA)
```

After this initial anonymization approach we end up with two datasets:

- demog_comp_phi_safe_icdA : no further action required, data is safe.
- demog_comp_phi_risky_icdA : on this dataset we will apply a suppression approach by removing ICD characters until desired threshold is reached.

### ICD B: 2 Characters removal

```{r}
# Remove one digit from the icd column for rows with more than one digit without counting other '*'
demog_comp_phi_risky_icdA_foricdB <- demog_comp_phi_risky_icdA %>%
   mutate(icd = ifelse(nchar(icd) > 3, paste0(substr(icd, 1, nchar(icd) - 1), ""), icd))

# Calculate the new k-anonymity of each row
demog_comp_phi_risky_icdA_foricdB <- demog_comp_phi_risky_icdA_foricdB %>%
  group_by(.dots = kanon_cols) %>% 
  mutate(k_anon = length(unique(!!sym(unique_idfr))))

# Filter the data frame to select rows with k-anonymity greater than or equal to the desired level, this patients are safe enough and no further action needs to be taken
demog_comp_phi_safe_icdB <- demog_comp_phi_risky_icdA_foricdB %>%
  filter(k_anon >= kanom_level)

# Filter the data frame to select rows with k-anonymity smaller than the desired level
demog_comp_phi_risky_icdB <- demog_comp_phi_risky_icdA_foricdB %>%
  filter(k_anon < kanom_level)

# checksum of rows 
nrow(demog_comp_phi_risky_icdA)
nrow(demog_comp_phi_safe_icdB)
nrow(demog_comp_phi_risky_icdB)
nrow(demog_comp_phi_safe_icdB)+
nrow(demog_comp_phi_risky_icdB)
```

After this initial anonymization approach we end up with two datasets:

- demog_comp_phi_safe_icdB : no further action required, data is safe.
- demog_comp_phi_risky_icdB : on this dataset we will apply a suppression approach by removing ICD characters until desired threshold is reached.

### ICD C: 3 Characters removal

```{r}
# Remove one digit from the icd column for rows with more than one digit without counting other '*'
demog_comp_phi_risky_icdA_foricdC <- demog_comp_phi_risky_icdB %>%
   mutate(icd = ifelse(nchar(icd) > 3, paste0(substr(icd, 1, nchar(icd) - 1), ""), icd))

# Calculate the new k-anonymity of each row
demog_comp_phi_risky_icdA_foricdC <- demog_comp_phi_risky_icdA_foricdC %>%
  group_by(.dots = kanon_cols) %>% 
  mutate(k_anon = length(unique(!!sym(unique_idfr))))

# Filter the data frame to select rows with k-anonymity greater than or equal to the desired level, this patients are safe enough and no further action needs to be taken
demog_comp_phi_safe_icdC <- demog_comp_phi_risky_icdA_foricdC %>%
  filter(k_anon >= kanom_level)

# Filter the data frame to select rows with k-anonymity smaller than the desired level
demog_comp_phi_risky_icdC <- demog_comp_phi_risky_icdA_foricdC %>%
  filter(k_anon < kanom_level)

# checksum of rows 
nrow(demog_comp_phi_risky_icdB)
nrow(demog_comp_phi_safe_icdC)
nrow(demog_comp_phi_risky_icdC)
nrow(demog_comp_phi_safe_icdC)+
nrow(demog_comp_phi_risky_icdC)
```

After this initial anonymization approach we end up with two datasets:

- demog_comp_phi_safe_icdC : no further action required, data is safe.
- demog_comp_phi_risky_icdC : on this dataset we will apply a suppression approach by generalizing eldery patients age until desired threshold is reached.

## 3) Final attempts of increassion kanom


### Elderly age generalization

All patients age>89 have been generalized to 99, the median age of all of them.

```{r}
nrow(demog_comp_phi_safe_icdC)
# this shows how 3 characters removal did not improve the kanom level not even for 1 row, therefore, we stick to the previous risky dataset we obtained, this is #demog_comp_phi_risky_icdB


# Since this is the last attempt, we totally remove ICD info from the final set of risky rows.

# first we calculate median age
median_elderly_age<-demog_comp_phi_risky_icdB[demog_comp_phi_risky_icdB$age > 89,'age']
median_elderly_age<-median(median_elderly_age$age)

demog_comp_phi_final_removal_for_elderly_removal <- demog_comp_phi_risky_icdB %>%
   mutate(age = if_else(age>89, '>89', as.character(age) ) )

# Calculate the new k-anonymity of each row
demog_comp_phi_final_removal_for_elderly_removal <- demog_comp_phi_final_removal_for_elderly_removal %>%
  group_by(.dots = kanon_cols) %>% 
  mutate(k_anon = length(unique(!!sym(unique_idfr))))

# Filter the data frame to select rows with k-anonymity greater than or equal to the desired level, this patients are safe enough and no further action needs to be taken
demog_comp_phi_safe_final_removal_for_elderly_removal <- demog_comp_phi_final_removal_for_elderly_removal %>%
  filter(k_anon >= kanom_level)

# Filter the data frame to select rows with k-anonymity smaller than the desired level
demog_comp_phi_risky_final_removal_for_elderly_removal <- demog_comp_phi_final_removal_for_elderly_removal %>%
  filter(k_anon < kanom_level)

# checksum of rows 
nrow(demog_comp_phi_risky_icdB)
nrow(demog_comp_phi_safe_final_removal_for_elderly_removal)
nrow(demog_comp_phi_risky_final_removal_for_elderly_removal)
nrow(demog_comp_phi_safe_final_removal_for_elderly_removal)+
nrow(demog_comp_phi_risky_final_removal_for_elderly_removal)
```

### Total ICD supression

```{r}
# Since this is the last attempt, we totally remove ICD info from the final set of risky rows.

demog_comp_phi_risky_icdB_for_total_icd_removal <- demog_comp_phi_risky_final_removal_for_elderly_removal %>%
   mutate(icd = '*' )

# Calculate the new k-anonymity of each row
demog_comp_phi_risky_icdB_for_total_icd_removal <- demog_comp_phi_risky_icdB_for_total_icd_removal %>%
  group_by(.dots = kanon_cols) %>% 
  mutate(k_anon = length(unique(!!sym(unique_idfr))))

# Filter the data frame to select rows with k-anonymity greater than or equal to the desired level, this patients are safe enough and no further action needs to be taken
demog_comp_phi_safe_final_total_icd_removal <- demog_comp_phi_risky_icdB_for_total_icd_removal %>%
  filter(k_anon >= kanom_level)

# Filter the data frame to select rows with k-anonymity smaller than the desired level
demog_comp_phi_risky_final_total_icd_removal <- demog_comp_phi_risky_icdB_for_total_icd_removal %>%
  filter(k_anon < kanom_level)

# checksum of rows 
nrow(demog_comp_phi_risky_final_removal_for_elderly_removal)
nrow(demog_comp_phi_safe_final_total_icd_removal)
print('After all attempts, this is the number of rows we cannot kanonimize anymore')
nrow(demog_comp_phi_risky_final_total_icd_removal)

nrow(demog_comp_phi_safe_final_total_icd_removal)+
nrow(demog_comp_phi_risky_final_total_icd_removal)
```

# Preparing final dataset

## Union all df containing safe data

```{r}
# Get a list of all objects in the environment
objs <- ls()

# Use grep to match the pattern "*safe*" and return the matching object names
safe_objs <- grep("*safe*", objs, value = TRUE)
safe_objs

# age needs to be same type across datasets that are going to be unioned
demog_comp_phi_safe <- demog_comp_phi_safe %>%
  mutate(age=as.character(age))

demog_comp_phi_safe_age <- demog_comp_phi_safe_age %>%
  mutate(age=as.character(age))

demog_comp_phi_safe_icdA <- demog_comp_phi_safe_icdA %>%
  mutate(age=as.character(age))

demog_comp_phi_safe_icdB <- demog_comp_phi_safe_icdB %>%
  mutate(age=as.character(age))

# this one is empty so we don't need it # demog_comp_phi_safe_icdC <- demog_comp_phi_safe_icdC %>%mutate(age=as.character(age))

demog_comp_phi_safe_final_removal_for_elderly_removal <- demog_comp_phi_safe_final_removal_for_elderly_removal %>%
  mutate(age=as.character(age))

demog_comp_phi_safe_final_total_icd_removal <- demog_comp_phi_safe_final_total_icd_removal %>%
  mutate(age=as.character(age))



# Cbind all safe datasets
demog_safe_final<-rbind(

demog_comp_phi_safe      %>% select(hosp_stay_id, hosp_mortality_bin, sex, icd, age, line),

demog_comp_phi_safe_age  %>% select(hosp_stay_id, hosp_mortality_bin, sex, icd, age, line),

demog_comp_phi_safe_icdA %>% select(hosp_stay_id, hosp_mortality_bin, sex, icd, age, line),

demog_comp_phi_safe_icdB %>% select(hosp_stay_id, hosp_mortality_bin, sex, icd, age, line),
# demog_comp_phi_safe_icdC %>% select(patient_ref, episode_ref, age, sex, exitus_bin, reg_date, icd), # this one is empty so we don't need it
demog_comp_phi_safe_final_removal_for_elderly_removal %>% select(hosp_stay_id, hosp_mortality_bin, sex, icd, age),

demog_comp_phi_safe_final_total_icd_removal %>% select(hosp_stay_id, hosp_mortality_bin, sex, icd, age),

)

# in the final checksum cbind of safe + number of rows we cannot kanonimize any more should add up the initial number of rows
nrow(demog_safe_final)
nrow(demog_comp_phi_risky_final_total_icd_removal)
nrow(demog_safe_final)+nrow(demog_comp_phi_risky_final_total_icd_removal)

# initial dataset
nrow(demog_comp_phi_extended)
```


# Re-structuring demog_safe_final into p_zero tables

## p_zero_phi.demog

```{r}
unique_hosp_patient<-unique(stay_events_phi%>%
  select(patient_id,hosp_stay_id))

unique_hosp_patient%<>%inner_join(demog_comp_phi_extended%>% 
  ungroup() %>%
  select(hosp_stay_id, nation_ref), by='hosp_stay_id')

# TOD!?!?! do we actually want to keep 
demog<-unique(demog_safe_final)%>%
inner_join(unique_hosp_patient, by='hosp_stay_id')%>% 
ungroup()%>%
select(patient_id,sex,nation_ref)

demog<-unique(demog)
```

## p_zero_phi.stay_events

every group is made by
patient_id, the dataframe is called unique_hosp_age, it also has a column called age
in age if whithin any group there is a >89, leave '>89' for the whole group
otherwise if there is a number followed by '*', leave that number followed by '*'

```{r}
# when running scripts several times, age and age_new need to be created for the first time, they cannot exist previously, this code prevents this chunk to crash
columns_to_remove <- c("age", "age_new")
# Check if columns exist and remove them if true
if (any(columns_to_remove %in% colnames(stay_events_phi))) {
  stay_events_phi <- select(stay_events_phi, -one_of(columns_to_remove))
}



unique_hosp_age<-unique(demog_safe_final%>% 
  ungroup()%>%
  select(hosp_stay_id,age))

unique_hosp_age<-unique_hosp_age%>%
  left_join(stay_events_phi, by='hosp_stay_id')%>%
  dplyr::arrange(patient_id,hosp_stay_id,age)%>%
  ungroup()%>%
  select(patient_id,hosp_stay_id,age)

# !! we could calculate age of a patient using admission dates even if one adm is deid
#therefore for those patients deid, we are deidentifying all ages for the whole patient
# meaning we apply the same age deid criteria for the whole patient


# if there are several ages per patient or stay, we take the minimum, if any one is >89, we put them all like that for that patient.

new_age_column <- unique_hosp_age  %>%
 group_by(patient_id) %>%
 mutate(age_mod = if(any(age == ">89")) ">89" else 
                   if(any(grepl("\\*", age))) as.character(min(as.numeric(gsub("\\D+", "", age[grepl("\\*", age)])))) 
                   else as.character(age))%>%
  mutate(age_mod = ifelse(nchar(age_mod) == 1, paste0(age_mod, '*'), age_mod))%>%
  ungroup()%>%
  select(hosp_stay_id,age_mod)%>%
  rename(age=age_mod)

# aggregating by hosp_stay_id, so we only get the min

new_age_column<-new_age_column%>%
  group_by(hosp_stay_id)%>%
  summarise(age_min=min(age))%>%
  select(hosp_stay_id,age_min)%>%
  rename(age=age_min)

stay_events_phi<-stay_events_phi%>%
  left_join(new_age_column, by='hosp_stay_id')

# Replace "*" with "5" in the age column
stay_events_phi$age_new <- gsub("\\*", "5", stay_events_phi$age)
```

## p_zero_phi.diag_events

```{r}
final_hosp_stay_icd<-unique(demog_safe_final%>%
  ungroup()%>%
  select(hosp_stay_id,icd,line))  

diag_events<-final_hosp_stay_icd%>%
  inner_join(demog_comp_phi%>%select(diag_type,reg_date,line), by = 'line')%>%
  select(hosp_stay_id, icd, diag_type, reg_date)

# QC of ICD chars supression

# Define df and col at the beginning
df <- diag_events
col <- "icd"

# Calculate the mean, median, and IQR of the number of characters in col
print(data.frame(mean = mean(nchar(df[[col]])), median = median(nchar(df[[col]])), IQR = IQR(nchar(df[[col]]))))

df <- diag_events_phi
col <- "icd"

# Calculate the mean, median, and IQR of the number of characters in col
print(data.frame(mean = mean(nchar(df[[col]])), median = median(nchar(df[[col]])), IQR = IQR(nchar(df[[col]]))))
```


## De-identify

!!TODO Create proper deided ids!
!! TODO join needs to be done by hosp adm id, it needs to be properly named.
!! TODO deid doesn't make sense anymore since patient_ref were changed

```{r}
demog_final_deid <- demog_final %>%
  left_join(deid_keys, by = "patient_ref")%>% # !! join by proved hosp adm id when available
  mutate(reg_date_deid = reg_date + weeks(week_multiples))%>%
  select(patient_deid,hosp_adm_deid,age,sex,exitus_bin,reg_date_deid,icd) # !!sele t proper deid id when available
  
```


# Inserting safe table in the database

```{r}
'
DROP TABLE IF EXISTS 
CREATE TABLE p_zero.demog
AS 
SELECT
patient_deid,

'
```


